---
title: "Project 4-5 Milestone 2"
author: "James Aniciete"
date: "March 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
# DO NOT ADD OR REVISE CODE HERE
knitr::opts_chunk$set(echo = FALSE)

# To knit instructions:  a = FALSE, b = TRUE
a <- FALSE
b <- TRUE
```

### Instructions

R markdown is a plain-text file format for integrating text and R code, and creating transparent, reproducible and interactive reports. An R markdown file (.Rmd) contains metadata, markdown and R code "chunks,"" and can be "knit" into numerous output types. Answer the test questions by adding R code to the fenced code areas below each item. There are questions that require a written answer that also need to be answered. Enter your comments in the space provided as shown below:

***Answer: (Enter your answer here.)    *** 

Once completed, you will "knit" and submit the resulting .html document and the .Rmd file. The .html will present the output of your R code and your written answers, but your R code will not appear.  Your R code will appear in the .Rmd file. The resulting .html document will be graded and a feedback report returned with comments.  Points assigned to each item appear in this template.

**Before proceeding, look to the top of the .Rmd for the (YAML) metadata block, where the *title*, *author* and *output* are given. Please change *author* to include your name, with the format 'lastName, firstName.'  Do not change the statement a <- TRUE.**

If you encounter issues with knitting the .html, please send an email to me or your TA.

In the Discussions area, I will open a discussion dedicated to this project. Please direct your questions there so we can discuss them as a class at the time you all work on the assignment. Your TA and myself will be monitoring the discussion

Each code chunk is delineated by six (6) backticks; three (3) at the start and three (3) at the end. After the opening ticks, arguments are passed to the code chunk and in curly brackets. **Please do not add or remove backticks, or modify the arguments or values inside the curly brackets.** An example code chunk is included here: 

```{r exampleCodeChunk, eval = a, echo = b}
# Comments are included in each code chunk, simply as prompts

#...R code placed here

#...R code placed here

```

-----
R code only needs to be added inside the code chunks for each assignment item. However, there are questions that follow many assignment items. Enter your answers in the space provided. An example showing how to use the template and respond to a question follows.
-----

Submit both the .Rmd and .html files for grading. You may remove the instructions and example problem above, but do not remove the YAML metadata block or the first, "setup" code chunk.  Address the steps that appear below and answer all the questions. Be sure to address each question with code and comments as needed.  You may use either base R functions or ggplot2 for the visualizations.

-----
Once you are ready to knit your code, delete lines 17 to 46.
-----

### INTRODUCTION

-----

Write one paragraph, introducing and presenting your project. Discuss the data set briefly, explaining what your data analysis entails. In one sentence, include the findings of your project, emphasizing at the most important finding.

*** Answer: This project discusses a company's revenues and costs based on time, region, product, and customers. The first question deals with an overview of the data, an analysis of the specific customers by manager and region, and scatterplots of multiple variables. The second question pertains to comparing net total to units and revenue. The third question is about comparing the distributions for each product A, B, and C, focusing on whether or not they appear to follow a normal distribution and have outliers. The fourth question dealt with identifying outliers for net total and revenue for each product. The fifth question dealt with comparing net total and revenue with each manager and the external factors to figure out if either could predict net total or revenue.   ***

The following code chunk will (a) load the ggplot2 and gridExtra packages, assuming each has been installed on your machine, (b) read-in the Accounts dataset, defining a new data frame, "mydata," (c) return the structure of that data frame, and (d) calculate new variables, VOLUME and RATIO. If either package has not been installed, you must do so first via *install.packages()*; e.g. *install.packages("ggplot2")*. You will also need to download the WidgetsInitial.csv from the course site to a known location on your machine.

```{r analysis_setup1, eval = b, echo = b, message = FALSE, warning = FALSE}

# a) Load the ggplot2 and gridExtra packages.

library(ggplot2)
library(gridExtra)

# b) Use read.csv() to read the WidgetsInitial.csv into R, assigning the data frame to "mydata."

mydata <- read.csv(file.path("F:/UIC Stuff/Spring 2018/STAT 382/Directory/WidgetsInitial.csv"), sep = ",", header = TRUE)

# c) Use the str() function to verify the structure of "mydata." You should have 793 observations
# of sixteen variables.

str(mydata)

# d) Define three new variables, STANDARDCOSTS based on Manager's Salary, NETTOTAL, UNITPROFIT as variables appended to the data frame "mydata."
mydata$STANDARDCOSTS <- mydata$SALARY/12/7
# should be mydata$STANDARDCOSTS <- mydata$SALARY/12/mydata$CUSTOMERS
mydata$NETTOTAL <- mydata$REVENUE - mydata$SECONDARYCOSTS - mydata$VARIABLECOSTS - mydata$STANDARDCOSTS
mydata$UNITPROFIT <- mydata$UNITREVENUE - mydata$UNITCOST
```

-----

(1)(a) (1 point) Use *summary()* to obtain and present descriptive statistics from mydata.  

```{r Part_1a, eval = b, echo = b}
summary(mydata)
```

**Question (1 point):  Briefly discuss the variable types and distributional implications such as potential skewness and outliers. Note that the measures will not be meaningful for all data.**

***Answer: In terms of variable types, there are nominal, interval, and ratio variables. Nominal variables include: STATE, REGION, SUBREGION, MANAGER, PRODUCT, and CUSTOMER. Interval variables include YEAR and MONTH. The rest of the variables are ratio variables. The data suggests that there will be positive skewness due to the mean being greater than the median for REVENUE, EXTERNAL FACTORS, SECONDARYCOSTS, VARIABLE COSTS, UNITREVENUE, NETTOTAL, and UNITPROFIT. There will be no skewness for UNITCOST since its mean is equal to its median. There will be negative skewness since the mean is less than the median for UNITS, SALARY, and STANDARDCOSTS. Potential outliers can be implied by a significant difference between the mean and median, so REVENUE, SECONDARYCOSTS, and NETTOTAL may have outliers.    *** 

(1)(b) (1 point) Generate a table of counts using MANAGER and CUSTOMER. Add margins to this table (Hint: There should be 15 cells in this table plus the marginal totals. Apply *table()* first, then pass the table object to *addmargins()*.  Lastly, present a barplot of these data.  
Generate a table of counts using REGION and CUSTOMER. Add margins to this table (Hint: There should be 15 cells in this table plus the marginal totals. Apply *table()* first, then pass the table object to *addmargins()*.  Lastly, present a barplot of these data.  


```{r Part_1b, eval = b, echo = b}
counts1 <- table(mydata$MANAGER, mydata$CUSTOMER)
addmargins(counts1)
barplot(counts1, ylim = c(0,140), cex.names = .8)

counts2 <- table(mydata$REGION, mydata$CUSTOMER)
addmargins(counts2)
barplot(counts2, ylim = c(0,140), cex.names = .8)
```

**Question (1 point):  Discuss the MANAGERs distribution of the Accounts.  What stands out about the distribution of Accounts by CUSTOMER?, Do the same By REGION?**

***Answer: What stands out about the distribution of Accounts by Customer is that each customer has a Sum of 72 accounts. What stands out about the distribution of Accounts by region is that each store has a very similar proportion of accounts from region to region. *** 

(1)(c) (1 point) Select a simple random sample of 100 observations from "mydata" and identify this sample as "work". Use *set.seed(123)* prior to drawing this sample. Do not change the number 123. (If you must draw another sample from mydata, it is imperative that you start with *set.seed(123)*, otherwise your second sample will not duplicate your first sample or the "work" sample used for grading your report.) 
Using this sample, construct a scatterplot matrix of variables Units, Revenue, Variable Costs, Standard Costs, Net Total  and Profit per unit with a command similar to *plot(work[, 2:6])* (these are the continuous variables excluding SALARY	EXTERNALFACTORS	SECONDARYCOSTS
and UNITPROFIT ). The sample "work" will not be used in the remainder of the assignment. 

```{r Part_1c, eval = b, echo = b}
set.seed(123)
work <- mydata[sample(1:nrow(mydata), 100, replace=FALSE),]
plot(work[,c(8, 9, 13, 17:19)]) # the x value is already in the data frame
```

-----

(2)(a) (1 point) Use "mydata" to plot NETTOTAL vs UNITS. 

```{r Part_2a, eval = b, echo = b}
plot(mydata$UNITS, mydata$NETTOTAL, xlab = "Units", ylab = "Net Total")
```

**Question (2 points):  What do you observe?

***Answer: I observe that the data seems to follow three different and increasing linear paths.    *** 

(2)(b) (2 points) Use "mydata" to plot NETTOTAL versus REVENUE. As an aid to interpretation, determine the maximum value of the ratio of NETTOTAL to REVENUE.  Add to the chart a straight line with zero intercept using this maximum value as the slope of the line. If you are using the 'base R' *plot()* function, you may use *abline()* to add this line to the plot. Use *help(abline)* in R to determine the coding for the slope and intercept arguments in the functions. If you are using ggplot2 for visualizations, *geom_abline()* should be used.
If you want you can use ggplots for this questions. Make sure that you include titles, legends and colors to make your presentation attractive. I would recommend to use the *brewercolor* package with different colors and types.

```{r Part_2b, eval = b, echo = b}
plot(mydata$REVENUE, mydata$NETTOTAL, main = "Net Total versus Revenue", xlab = "Revenue", ylab = "Net Total")
maxratio <- max(mydata$NETTOTAL/mydata$REVENUE)
abline(a =0, b = maxratio, col = 'darkred') 
```

**Question (2 points):  How does the variability in this plot differ from the plot in (a)?  Compare the two displays.  Keep in mind that NETTOTAL is a part of REVENUE when there is Profit.**

***Answer: This plot has much less variability since the points seem to follow one linear path compared to the three linear paths seen in (a). This plot's x-axis is revenue while the plot in (a)'s x-axis was units. Therefore, this plot does not account for any of the costs, which could explain why the points only follow one linear path.    *** 

-----

(3)(a1) (2 points) Use "mydata" to create a multi-figured plot with histograms, boxplots and Q-Q plots of REVENUE differentiated by PRODUCT. This can be done using *par(mfrow = c(3,3))* and base R or *grid.arrange()* and ggplot2. The first row would show the histograms, the second row the boxplots and the third row the Q-Q plots. Be sure these displays are legible. Note that there are two ways to do this, you can either manipulate the attributes of the yaxis or you can manipulate the arguments of the Rmarkdown chunk, to ensure that the graphs are not shrinked while knitting. If you have issues knitting your graphs, then let me know especially if you try to create a pdf file and you use a MAC.

```{r Part_3a1, eval = b, echo = b}
par(mfrow=c(3,3))

productA <- mydata[which(mydata$PRODUCT == 'Tablet A'), ]
productB <- mydata[which(mydata$PRODUCT == 'Tablet B'), ]
productC <- mydata[which(mydata$PRODUCT == 'Tablet C'), ]

hist(productA$REVENUE, xlim = c(0, 150000), ylim = c(0,45), main = "Histogram of Product A's Revenue", xlab = "Product A's Revenue", col = "red")
hist(productB$REVENUE, xlim = c(0, 150000), ylim = c(0,45), main = "Histogram of Product B's Revenue", xlab = "Product B's Revenue", col = "green")
hist(productB$REVENUE, xlim = c(0, 150000), ylim = c(0,45), main = "Histogram of Product C's Revenue", xlab = "Product B's Revenue", col = "blue")
boxplot(productA$REVENUE, main = "Boxplot of Product A's Revenue", ylim = c(0,200000), col = "red")
boxplot(productB$REVENUE, main = "Boxplot of Product B's Revenue", ylim = c(0,200000), col = "green")
boxplot(productC$REVENUE, main = "Boxplot of Product C's Revenue", ylim = c(0,200000), col = "blue")
qqnorm(productA$REVENUE, main = "Q-Q Plot of Product A's Revenue", ylim = c(0,200000), col = "red")
qqnorm(productB$REVENUE, main = "Q-Q Plot of Product B's Revenue", ylim = c(0,200000), col = "green")
qqnorm(productC$REVENUE, main = "Q-Q Plot of Product C's Revenue", ylim = c(0,200000), col = "blue")
# Product A = red, Product B = green, Product C = blue
```
(3)(a2) (2 points) Use "mydata" to create a multi-figured plot with histograms, boxplots and Q-Q plots of NETTOTAL differentiated by PRODUCT. This can be done using *par(mfrow = c(3,3))* and base R or *grid.arrange()* and ggplot2. The first row would show the histograms, the second row the boxplots and the third row the Q-Q plots. Be sure these displays are legible.  

```{r Part_3a2, eval = b, echo = b}
par(mfrow=c(3,3))
hist(productA$NETTOTAL, main = "Histogram of Product A's Net Total", xlab = "Product A's Net Total", xlim = c(0, 200000), ylim = c(0,40), col = "red")
hist(productB$NETTOTAL, main = "Histogram of Product B's Net Total", xlab = "Product B's Net Total", xlim = c(0, 200000), ylim = c(0,40), col = "green")
hist(productC$NETTOTAL, main = "Histogram of Product C's Net Total", xlab = "Product C's Net Total", xlim = c(0, 200000), ylim = c(0,40), col = "blue")
boxplot(productA$NETTOTAL, main = "Boxplot of Product A's Net Total", xlab = "Product A's Net Total", ylim = c(0,200000), col = "red")
boxplot(productB$NETTOTAL, main = "Boxplot of Product B's Net Total", xlab = "Product B's Net Total", ylim = c(0,200000), col = "green")
boxplot(productC$NETTOTAL, main = "Boxplot of Product C's Net Total", xlab = "Product C's Net Total", ylim = c(0,200000), col = "blue")
qqnorm(productA$NETTOTAL, main = "Q-Q Plot of Product A's Net Total", xlab = "Product A's Net Total", ylim = c(0,200000), col = "red")
qqnorm(productB$NETTOTAL, main = "Q-Q Plot of Product B's Net Total", xlab = "Product B's Net Total", ylim = c(0,200000), col = "green")
qqnorm(productC$NETTOTAL, main = "Q-Q Plot of Product C's Net Total", xlab = "Product C's Net Total", ylim = c(0,200000), col = "blue")
```

**Question (2 points): Compare the displays.  How do the distributions compare to normality? Give complete answers explaining what are your findings and why?**

***Answer: All of the distributions appear to be normal distributions because the shape of their Q-Q plots are similar to that of the normal distribution's cdf. Product A's distribution most closely resembles the normal distribution since its curves are the most defined while Product C's distribution least resembles the normal disttribution since its curves are not as smooth as the other two distributions' curves. *** 


(3)(b) (2 points) Use the boxplots to identify NETTOTAL and REVENUE outliers. Present the Accounts with these outlying RATIO values along with their associated variables in "mydata." Hint:  Construct a listing of the observations using the *kable()* function. The use of kable() is not a requriement, it is rather a suggestion, and it is expected you will research it. If you have issues with finding the package ( it doesn't work in all Rstudio versions) abort the process, and find an alternative. 

```{r Part_3b, eval = b, echo = b}
a_nettotal_outliers <- boxplot.stats(productA$NETTOTAL/mydata$NETTOTAL)$out
if (length(a_nettotal_outliers) == 0) {a_nettotal_outliers <- 0}
b_nettotal_outliers <- boxplot.stats(productB$NETTOTAL/mydata$NETTOTAL)$out
if (length(b_nettotal_outliers) == 0) {b_nettotal_outliers <- 0}
c_nettotal_outliers <- boxplot.stats(productC$NETTOTAL/mydata$NETTOTAL)$out
if (length(c_nettotal_outliers) == 0) {c_nettotal_outliers <- 0}

a_revenue_outliers <- boxplot.stats(productA$REVENUE/mydata$REVENUE)$out
if (length(a_revenue_outliers)==0) {a_revenue_outliers <- 0}
b_revenue_outliers <- boxplot.stats(productB$REVENUE/mydata$REVENUE)$out
if (length(b_revenue_outliers)==0) {b_revenue_outliers <- 0}
c_revenue_outliers <- boxplot.stats(productC$REVENUE/mydata$REVENUE)$out
if (length(c_revenue_outliers)==0) {c_revenue_outliers <- 0}

max.length <- max(length(a_nettotal_outliers), length(b_nettotal_outliers), length(c_nettotal_outliers), length(a_revenue_outliers), length(b_revenue_outliers), length(c_revenue_outliers))
a_nettotal_outliers <- c(a_nettotal_outliers, rep(NA, max.length-length(a_nettotal_outliers)))
b_nettotal_outliers <- c(b_nettotal_outliers, rep(NA, max.length-length(b_nettotal_outliers)))
c_nettotal_outliers <- c(c_nettotal_outliers, rep(NA, max.length-length(c_nettotal_outliers)))
a_revenue_outliers <- c(a_revenue_outliers, rep(NA, max.length-length(a_revenue_outliers)))
b_revenue_outliers <- c(b_revenue_outliers, rep(NA, max.length-length(b_revenue_outliers)))
c_revenue_outliers <- c(c_revenue_outliers, rep(NA, max.length-length(c_revenue_outliers)))

outliers <- data.frame(a_nettotal_outliers, b_nettotal_outliers, c_nettotal_outliers, a_revenue_outliers, b_revenue_outliers, c_revenue_outliers)
library(knitr)
kable(outliers)
```

**Question (1 point):  What are your observations regarding the results in (3)(b)?  **

***Answer: Product B's Revenue had the least outliers while Product A's Net Total had the most outliers.    ***

-----

(4)(a) (3 points) With "mydata," display three separate sets of side-by-side boxplots for NETTOTAL and REVENUE differentiated by MANAGER. Show six boxplots for NETTOTAL in one display and SIX boxplots for REVENUE (making two separate displays). Also, create two separate scatterplots of NETTOTAL and REVENUES versus EXTERNALFACTORS. Present these displays in **one graphic**, the boxplots in one row and the scatterplots in a second row. Use ggplot2 for this.


```{r Part_4a, eval = b, echo = b}
require(ggplot2)
require(gridExtra)
require(RColorBrewer)
g1 <- ggplot(mydata, aes(x=MANAGER, y = NETTOTAL, fill = MANAGER)) + geom_boxplot() + ggtitle("Net Total vs Manager") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_fill_brewer(palette = "Set3")
g2 <- ggplot(mydata, aes(x=MANAGER, y = REVENUE, fill = MANAGER)) + geom_boxplot() + labs(title = "Revenue vs Manager") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_fill_brewer(palette = "Set3")
# Set 3 is one of the only color palettes to have 11 colors - the others typically have 9
g3 <- ggplot(mydata, aes(x = EXTERNALFACTORS, y = NETTOTAL)) + geom_point(aes(colour = PRODUCT)) + labs(title = "Net Total vs External Factors")
g4 <- ggplot(mydata, aes(x = EXTERNALFACTORS, y = REVENUE, fill = PRODUCT)) + geom_point(aes(colour = PRODUCT)) + ggtitle("Revenue vs External Factors") 
# External factors colored by Product
grid.arrange(g1, g2, g3, g4)

```

**Question (3 points) How well do you think these variables would perform as predictors of NETTOTAL or REVENUE?**

***Answer: Since most of the boxplots cover about the same interquartile range, I do not think manager is a good predictor of net total or revenue. Since the scatterplots do not show an overall trend, external factors is not a good predictor of net total or revenue.***

-----

(5)(a) (3 points) Use *aggregate()* with "mydata" to compute the mean values of REVENUE, NETTOTAL and UNITS for each combination of MANAGER, and WIDGET. Then, using *matrix()*, create matrices of the mean values. Using the "dimnames" argument within *matrix()* or the *rownames()* and *colnames()* functions on the matrices, label the rows by PRODUCT and columns by MANAGER. Present the three matrices. You do not need to be concerned with the number of digits presented.

```{r Part_5a, eval=b, echo=b}
noquote("Mean Units Matrix:")
agg_units <- aggregate(mydata$UNITS, by = list(mydata$MANAGER, mydata$PRODUCT), mean)
matrix_units <- data.matrix(agg_units)
matrix_units <- matrix_units[,3]
matrix_units <- matrix(matrix_units,nrow=3)
colnames(matrix_units) <- unique(mydata$MANAGER)
rownames(matrix_units) <- unique(mydata$PRODUCT)
matrix_units
cat("\n") # line break

noquote("Mean Revenue Matrix:")
agg_rev <- aggregate(mydata$REVENUE, by= list (mydata$MANAGER, mydata$PRODUCT), mean)
matrix_rev <- data.matrix(agg_rev)
matrix_rev <- matrix_rev[,3]
matrix_rev <- matrix(matrix_rev,nrow=3)
colnames(matrix_rev) <- unique(mydata$MANAGER)
rownames(matrix_rev) <- unique(mydata$PRODUCT)
matrix_rev
cat("\n")

noquote("Mean Net Total Matrix:")
agg_nettotal <- aggregate(mydata$NETTOTAL, by = list(mydata$MANAGER, mydata$PRODUCT), mean)
matrix_nettotal <- data.matrix(agg_nettotal)
matrix_nettotal <- matrix_nettotal[,3]
matrix_nettotal <- matrix(matrix_nettotal,nrow=3)
colnames(matrix_nettotal) <- unique(mydata$MANAGER)
rownames(matrix_nettotal) <- unique(mydata$PRODUCT)
matrix_nettotal

# Calculations for Question 1 below:
#colSums(matrix_units)
#colSums(matrix_rev)
#colSums(matrix_nettotal)
```

(5)(b) (3 points) Present three graphs. Each graph should be generated with three separate lines appearing, one for each PRODUCT. The first should show mean NETTOTAL versus CUSTOMER; the second, average REVENUE versus CUSTOMER; the third, UNITS versus CUSTOMER. This may be done with the 'base R' *interaction.plot()* function or with ggplot2.


```{r Part_5b, eval=b, echo=b}
g_nettotal <- ggplot(data = mydata, aes(x = CUSTOMER, y = NETTOTAL, group = PRODUCT, colour = PRODUCT)) + stat_summary(fun.y = "mean", geom = "line") + ggtitle("Mean Net Total vs Customer")
g_rev <- ggplot(data = mydata, aes(x = CUSTOMER, y = REVENUE, group = PRODUCT, colour = PRODUCT)) + stat_summary(fun.y = "mean", geom = "line") + ggtitle("Mean Revenue vs Customer")
g_units <- ggplot(data = mydata, aes(x = CUSTOMER, y = UNITS, group = PRODUCT, colour = PRODUCT)) + stat_summary(fun.y = "mean", geom = "line") + ggtitle("Mean Units vs Customer")

g_nettotal
g_rev
g_units

# Method 2 - Interaction Plot
#interaction.plot(x.factor = mydata$CUSTOMER, trace.factor = mydata$PRODUCT, response = mydata$NETTOTAL, FUN = mean, xlab = "Customer", ylab = "Mean Net Total", main = "Mean Net Total vs Customer by Product", trace.label = "Product", cex.axis = .6)
#interaction.plot(x.factor = mydata$CUSTOMER, trace.factor = mydata$PRODUCT, response = mydata$REVENUE, FUN = mean, xlab = "Customer", ylab = "Mean Units", main = "Mean Revenue vs Customer by Product", trace.label = "Product", cex.axis = .6)
#interaction.plot(x.factor = mydata$CUSTOMER, trace.factor = mydata$PRODUCT, response = mydata$UNITS, FUN = mean, xlab = "Customer", ylab = "Mean Units", main = "Mean Units vs Customer by Product", trace.label = "Product", cex.axis = .6)

# For Question 4:
#g_salary <- ggplot(data = mydata, aes(x = SALARY, y = REVENUE)) + stat_summary(fun.y = "mean", geom = "line") + ggtitle("Mean Revenue vs Salary")
#g_salary
```
(6) (Extra credit 20 points) After you review all the different presentation, there is still a lot of different perspectives that you can take to analyze the data. Choose any type of visual representation that you find fit to understand better predictors of High NETTOTAL and high REVENUE.

**Conclusions**

Please respond to each of the following questions (10 points total):

**Question 1) (5 points)	Where you able to find clear evidence of who is the best performing manager? What is the best performing Widget ? What is the best Manager? Is your study successful? If not what is the reason that this was not possible?**

***Answer: By summing the net totals for each manager, it appears that Larry Main was the best performing manager. Also, I believe that the best performing product was Product C, which had the highest mean net totals and mean revenues of all three products despite the fact that its mean units were lower for some customers. However, the possible effects of the external factors on the net totals would prevent me from drawing a clear conclusion for either best manager or product. Thus, my study was partially successful in that I was able to find out who I believe the best manager and product were. Now, I would have to further investigate the external factors before I could come to a clear conclusion.    ** 


** Question 2) (3 points) Setting the Accounts data and analysis aside, if you were presented with an overall histogram and summary statistics from a sample and no other information, what questions might you ask before accepting them as representative of the sampled population? In addition, assume you receive a histogram and a boxplot for each manager's accounts, can you comment on the Manager's performance and his/hers increase of sales over time? Why or why not?**

***Answer: Given an overall histogram and summary statistics from a sample, I would ask about how many observations are in the sample. If there are not enough observations, the sample will not be representative of the population in question. Given a histogram and a boxplot for each manager's accounts, one cannot comment on the manager's performance or his/her increase of sales over time. One would need to consider external factors like inflation and the time of the year. Prices may increase due to inflation and sales might increase before Christmas for instance, so one would need to know about the external factors before evaluating a manager's performance.**


**Question 3)  (2 points)	We have already reviewed the creation of Dashboards in class. After you complete your study, explain which of the graphs/charts above you would include in your Dashboard and why? Are there any other graphs you would consider?**

***Answer: In a dashboard, I would include: the barplot comparing region and customer from part 1b, the histograms of each product's revenue and net total from part 3, all of the graphs from 4a, and the graphs from 5b. I believe these graphs/charts would best summarize my observations from this study. I would also consider graphs comparing regional net totals and revenues of each product and also time-series graphs showing product and manager performances throughout the year.**

**Question 4) (5 extra points) Indicate, what other information would be important to know to understand better the future performance of a manager and a region? Which of the Tablets is more profitable taking into account its price? Does the salary of a manager is a strong indicator of his/her performance? Does it affect the revenue positively or negatively?**

***Answer: Additional information on the external factors, about how the given variables change with respect to time, and the total population sizes of each region would be important to know to better understand the future performance of a manager and a region. Product C was the most profitable taking into account its price. Yes, salary of a manager is a strong indicator of his/her performance in this study although Mark Lane would be an outlier. Mark Lane's summed net total was the second highest, yet he does not have one of the highest salaries. Generally, there is a trend for higher salaries of managers to affect revenue negatively. **